\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{top=1.2cm,bottom=1.5cm,left=1.2cm,right=1.2cm}
\usepackage{hyperref}
\usepackage{titlesec}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% \begin{center}
%     {\LARGE \textbf{Mirza Mohd Ashran Baig}} \\[4pt]
%     Bengaluru, India \quad | \quad +91-7408309214 \quad | \quad 
%     \href{mailto:ashranbaig1310@gmail.com}{ashranbaig1310@gmail.com}
% \end{center}
\begin{center}
    {\Huge \textbf{Mirza Mohd Ashran Baig}} \\[6pt]
    Bengaluru, India \,|\, +91-xxxxxxxxxx \,|\, 
    \href{mailto:ashranbaig1310@gmail.com}{ashranbaig1310@gmail.com} \,|\, 
    \href{https://www.linkedin.com/in/ashranbaig}{LinkedIn} \,|\, 
    \href{https://github.com/ashranbaig}{GitHub}
\end{center}

\vspace{0.3cm}

\section*{Objective}

Senior DevOps Engineer with 5+ years of experience leading teams in architecting and managing enterprise-scale, cloud-native infrastructures across Azure, AWS, and GCP. Proven expertise in automating deployments with Terraform, Kubernetes, and CI/CD pipelines to support mission-critical applications. Skilled at implementing SRE practices to ensure high availability, security, and cost-optimized operations. Strong track record of collaborating with globally distributed teams to deliver resilient and scalable enterprise platforms.


\section*{Experience}

\textbf{Hexaware Technologies} \hfill Aug 2024 -- Present \\
\emph{Senior DevOps Engineer}  
\begin{itemize}[leftmargin=*]
\item {Led engineering efforts to design and maintain enterprise-scale data pipelines using Snaplogic and Snowflake, enabling efficient AI-driven analytics delivery for global business operations.}
\item {Automated end-to-end CI/CD pipelines via Azure DevOps (YAML), using S3, EC2 instances, IAM, SageMaker, AWS WAF, Lambda, EKS, ECS, EBS, Amazon Athena, AWS Glue, driving higher deployment frequency, production stability, and reducing release cycle time by 30\%.}
\item {Provisioned and standardised enterprise infrastructure using Terraform with reusable modules and environment-specific configurations across multi-tiered systems.}
\item {Managed Azure cloud infrastructure with a focus on high availability, enterprise performance SLAs, and security hardening for business-critical systems.}
\item {Implemented proactive monitoring and observability using Prometheus, Azure Monitor, Datadog, Splunk, Dynatrace,ELK and Amazon CloudWatch, ensuring 99.95\% uptime and enabling predictive incident detection.}
\item {Collaborated with cross-functional global teams, including data engineering, data scientists, QA, and architecture, to deliver resilient, large-scale AI/ML applications and data products.}

\end{itemize}


\textbf{Stovl / Eximietas Design} \hfill Sep 2023 -- Jun 2024 \\
\emph{  Associate DevOps Engineer}  
\begin{itemize}[leftmargin=*]
 \item {Engineered enterprise CI/CD pipelines using GitLab CI for a global EMM solution, integrating SAST, test automation, and approval workflows.}
    \item {Provisioned and scaled cloud resources via Terraform and deployed microservices with Docker and Helm charts on GKE clusters.}
    \item {Applied Infrastructure-as-Security principles by enforcing enterprise-grade policies through IaC, minimizing misconfiguration and compliance risks.}
    \item {Implemented a full observability stack with Google Cloud Monitoring to ensure availability, performance, and resilience of enterprise workloads.}
    \item {Performed cost optimization and capacity forecasting using load/time-based metrics to support enterprise-level financial planning.}

\end{itemize}

\textbf{KPMG Global Services} \hfill Jul 2022 -- Aug 2023 \\
\emph{Associate Consultant (DevOps)}  
\begin{itemize}[leftmargin=*]
 \item {Delivered Infrastructure-as-Code solutions, automated CI/CD pipelines, and artifact workflows for a large-scale supply chain management platform.}
    \item {Enabled developer productivity at scale by conducting Terraform and Azure DevOps training for cross-functional engineering teams.}
    \item {Enhanced enterprise reliability by implementing SLOs, improving monitoring coverage, and establishing root cause analysis practices across production systems.}
      \item Supported dev team enablement by conducting Terraform and Azure DevOps training.

      \newpage

\end{itemize}
\textbf{Mindtree} \hfill Jan 2020 -- Jul 2022 \\
\emph{DevOps Engineer / Site Reliability Engineer}  
\begin{itemize}[leftmargin=*]
 \item {Supported 24/7 operations for mission-critical enterprise workloads, collaborating with global delivery teams in the Middle East region.}
    \item {Improved CI/CD reliability by remediating Jenkins/Azure DevOps pipeline failures and performing root cause analysis for build stability.}
    \item {Applied SRE practices including incident response, monitoring, and capacity planning for enterprise-scale production environments.}
    \item {Enabled predictive auto-scaling using traffic-based metrics with cost-control thresholds, optimizing performance and spend for high-volume systems.}
    \item {Achieved 40\% reduction in downtime and security incidents through proactive DevSecOps automation and policy enforcement.}

\end{itemize}

\section*{Key Projects}
\textbf{ Cadbury – My Personal AI Agentic Manager(Personal Project) } \hfill 2024 -- Present   
\href{https://huggingface.co/spaces/ashranbaig/Cadbury-My-Manager}{\texttt{Link to the Project}}  
\begin{itemize}[leftmargin=*]
  \item Designed and developed an AI-powered personal assistant named \emph{Cadbury}, capable of handling all my professional queries.
  \item Integrated large language model (LLM) capabilities with agentic workflows, enabling context-aware responses and task automation.  
  \item Demonstrated entrepreneurial initiative by independently building an AI solution that enhances productivity, reflecting strong problem-solving and innovation skills.
  \item {Integrated learnings from personal DevOps projects (IaC automation, Kubernetes observability stack, predictive scaling strategies) into enterprise solutions, improving cost efficiency and operational reliability.}

\end{itemize}


\textbf{ Enterprise Data Pipeline Modernization- The Carlyle Group } \hfill 2024 -- Present  

\begin{itemize}[leftmargin=*]

  \item Led a team of four engineers to design and maintain scalable data pipelines for The Carlyle Group.
  \item Orchestrated ETL workflows on Azure DevOps and managed AI-integrated analytics with Snowflake and Sigma.
  \item Automated CI/CD processes and provisioned Azure infrastructure using reusable Terraform modules.
  \item Implemented proactive monitoring with Prometheus, sustaining 99.95\% uptime.
  \item Collaborated with data, QA, and architecture teams to deploy business-critical models.
  \item Drove operational reliability and enabled advanced, AI-powered analytics for enterprise reporting.
\end{itemize}

\textbf{ Multinational Hotel  Booking Platform in the Middle East } \hfill Jan 2020 -- Jul2022  

\begin{itemize}[leftmargin=*]

\item {Led a cross-functional team of 4 DevOps/SRE engineers, overseeing CI/CD pipelines, infrastructure automation, and observability initiatives.}
\item {Remediated CI/CD instability across Jenkins and Azure DevOps, improving release reliability and developer productivity.}
\item {Managed auto-healing infrastructure and applied SRE principles including incident management, SLO-based monitoring, and capacity planning.}
\item {Implemented predictive auto-scaling strategies and proactive cost-control mechanisms, optimizing hosting costs during peak traffic surges.}

\end{itemize}


\section*{Education}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{B.Tech, Computer Science Engineering} & 2016--2020 \\
  Kalinga Institute of Industrial Technology, Odisha & \\
  CGPA: 7.10/10 & \\
  \\[-2pt] % small space between entries
  \textbf{B.Tech (5th Semester), Computer Science Engineering} & 2019 \\
  Nanhua University, Chiayi, Taiwan & \\
\end{tabular*}


\section*{Certifications}
Google Professional: Cloud DevOps Engineer \quad    Microsoft Certified: DevOps Engineer Expert \quad

\end{document}
