%-------------------------
% Resume in Latex
% Author : Mirza Mohd Ashran Baig
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=0.6cm, top=0.5cm, right=0.6cm, bottom=0.5cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands

\newcommand{\resumeCP}[1]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}
    \end{tabular*}
    \vspace{-1mm}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeAchieve}[2]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\textbf{:}\hspace{0.3mm}#2 
    \end{tabular*}
    \vspace{-1.4mm}
}

\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1},\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Mirza Mohd Ashran Baig} % Your Name
\newcommand{\course}{} % Your Course
\newcommand{\roll}{} % Your Roll No.
\newcommand{\phone}{XXXXXXXXXX} % Your Phone Number
\newcommand{\emaila}{ashranbaig1310@gmail.com} %Email 1
\newcommand{\emailb}{ashranbaig1310@gmail.com} %Email 2
\newcommand{\github}{ashranbaig} %Github
\newcommand{\website}{link to your portfolio if any} %Website
\newcommand{\linkedin}{ashranbaig} %linkedin




\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------
\parbox{\dimexpr\linewidth\relax}{
\begin{tabularx}{\linewidth}{L r}
  \textbf{\LARGE \name} & +91-\phone\\
  
  \course &  \href{mailto:\emailb}{\emailb}\\
  {B.Tech - Computer Science Engineering} &  \href{https://github.com/ashranbaig}{GitHub} \\
%   $|$ \href{\website}{Website}\\
  {Kalinga Institute Of Industrial Technology,Bhubaneswar, Odisha} & \href{https://www.linkedin.com/in/ashranbaig/}{Linkedin}
\end{tabularx}
}

\vspace{-1mm}

%-----------EDUCATION-----------------

\section{\textbf{Education}}
\vspace{2.5mm}
\setlength{\tabcolsep}{6pt} % Default value: 6pt
% \renewcommand{\arraystretch}{1.1} % Default value: 1
\small{\begin{tabularx}
{\dimexpr\textwidth-2mm\relax}{|c|C|c|c|}
  \hline
  \textbf{Degree } & \textbf{Institute/Board} & \textbf{CGPA/Percentage} & \textbf{Year}\\
  \hline
  Bachelor of Technology & Kalinga Institute Of Industrial Technology,Bhubaneswar, Odisha & 7.10/10  & 2016-20\\
  
  %\hline
  %Minor in CSE & Indian Institute of Technology, Ropar & 8.52 %(Till 6th Sem) & 2018-2022\\
 
  \hline
  Senior Secondary & St. Joseph's School (ISC) & 76.75 \% & 2016 \\
  \hline
  Secondary & St. Joseph's School (ICSE) & 83.66\% & 2014 \\
  \hline
\end{tabularx}}
\vspace{0mm}

%-----------EXPERIENCE-----------------
\section{\textbf{Work Experience}}
  \resumeSubHeadingListStart
\vspace{2.5mm}
    \resumeSubheading
      {Hexaware Technologies }{Bengaluru, Karnataka}
      {Senior DevOps Engineer }{Aug 2024 - Present}
      \vspace{1.5mm}
      \resumeItemListStart
    \item {Designed and maintained scalable data pipelines using Snaplogic and Snowflake for efficient analytics delivery.}
  \item Automated CI/CD pipelines via Azure DevOps (YAML), improving deployment frequency and production stability.
  \item Provisioned infrastructure using Terraform with modules for reusability and environment-specific configurations.
  \item Managed Azure infrastructure with emphasis on high availability, performance SLAs, and security hardening.
  \item Monitored production systems using Prometheus and Azure Monitor; maintained 99.95\% uptime metrics.
  \item Collaborated with data engineering, QA, and architecture teams to deploy business-critical models.
    \resumeItemListEnd
  
    

    % \item {More work done } .
  \resumeSubHeadingListEnd
\vspace{-4.5mm}

\resumeSubHeadingListStart
\vspace{2.5mm}
    \resumeSubheading
      {Stovl / Eximietas Design }{Bengaluru, Karnataka}
      {Associate DevOps Engineer }{Sep 2023 - June 2024}
      \vspace{1.5mm}
      \resumeItemListStart
     \item Engineered CI/CD pipelines using GitLab CI for a global EMM solution, integrating SAST, test automation, and approvals.
  \item Provisioned cloud resources via Terraform and deployed apps with Docker and Helm charts on GKE.
  \item Applied Infrastructure-as-Security principles: enforced policies through IaC, minimized misconfiguration risk.
  \item Implemented observability stack using Google Cloud Monitoring to track infra and container health.
  \item Conducted cost analysis and capacity forecasting based on load/time-based trend metrics.
    \resumeItemListEnd
     
    
    % \item {More work done } .
  \resumeSubHeadingListEnd

\resumeSubHeadingListStart
\vspace{2.5mm}
    \resumeSubheading
      {KPMG Global Services }{Bengaluru, Karnataka}
      {Associate DevOps Consultant }{Jul 2022 - Aug 2023}
      \vspace{1.5mm}
      \resumeItemListStart
  \item Delivered IaC, automated pipelines, and artifact workflows for supply chain management platform.
  \item Supported dev team enablement by conducting Terraform and Azure DevOps training.
  \item Enhanced reliability via implementation of SLOs, monitoring coverage, and root cause practices.

    \resumeItemListEnd
  

    
    
    % \item {More work done } .
  \resumeSubHeadingListEnd

   \resumeSubHeadingListStart
\vspace{2.5mm}
    \resumeSubheading
      {Mindtree }{Bengaluru, Karnataka}
      {DevOps Engineer / Site Reliability Engineer}{Jan 2020 - Jul 2022}
      \vspace{1.5mm}
      \resumeItemListStart
    \item Supported 24/7 operations for critical production workloads, collaborating with Middle East delivery teams.
  \item Improved pipeline reliability by remediating Jenkins/Azure DevOps failures and root causing build issues.
  \item Applied SRE principles — incident response, monitoring, capacity planning.
  \item Enabled traffic-based auto-scaling using predictive metrics with cost-control thresholds.
  \item Achieved 40\% reduction in time and security issues via proactive DevSecOps policy automation.
    \resumeItemListEnd
  
    
    % \item {More work done } .
  \resumeSubHeadingListEnd

% %-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{2.5mm}
\resumeSubHeadingListStart
\resumeProject
      {Enterprise Data Pipeline Modernization- AI-Driven Analytics Automation for The Carlyle Group} %Project Name
      {USA} %Project Name, Location Name
      {Aug 2024 - Present} %Event Dates

      \resumeItemListStart
        \item{Led a team of four engineers to design and maintain scalable data pipelines for The Carlyle Group, orchestrating ETL workflows on Azure DevOps and managing AI-integrated analytics with Snowflake and Sigma. Automated CI/CD processes, provisioned Azure infrastructure using Terraform modules, and implemented proactive monitoring with Prometheus (99.95\% uptime). Collaborated with data, QA, and architecture teams to deploy business-critical models, driving operational reliability and enabling advanced, AI-powered analytics for enterprise reporting.}
        
    \resumeItemListEnd
    \newpage
\vspace{2.5mm}
    
    \resumeProject
      {Multinational Hotel  Booking Platform in the Middle East} %Project Name
      {Dubai} %Project Name, Location Name
      {Jan 2020 - Jul 2022} %Event Dates
     {\href{https://www.jumeirah.com/en/}{\textbf{link to the project}}} %Website
    % {}
      \resumeItemListStart
        \item{I led a cross-functional team of 4 DevOps/SRE engineers, overseeing continuous integration pipelines, infrastructure automation, and observability initiatives. Key responsibilities included remediating CI/CD instability (Jenkins, Azure DevOps), managing auto-healing infrastructure, and applying SRE principles like incident management, SLO-based monitoring, and capacity planning. We implemented predictive auto-scaling strategies and proactive cost control mechanisms to optimize hosting costs during traffic surges.

Our DevSecOps automation initiative reduced security incidents and manual patching overhead, resulting in a 40\% improvement in operational efficiency and enhanced platform uptime during seasonal high-load periods.}
        
    \resumeItemListEnd


     

\vspace{1mm}
\resumeSubHeadingListStart
\section{\textbf{Technical Expertise}}
\item{\textbf{Cloud Platforms: }}{Azure (IaaS, PaaS), GCP (GKE), Azure Migrate}
\item{\textbf{Infrastructure as Code: }}{Terraform, Bicep, ARM templates, PowerShell, Azure CLI}
\item{\textbf{CI/CD Engineering: }}{Azure DevOps (YAML), GitLab CI, Jenkins, GitHub Actions}
\item{\textbf{Containers \& Orchestration: }}{Docker, Kubernetes (GKE), Helm}
\item{\textbf{Monitoring \& Logs}}{Prometheus, Azure Monitor, Google Cloud Monitoring}
\item{\textbf{Networking \& Security}}{VNets, ExpressRoute, vWAN, NSGs, NVAs}
\item{\textbf{Version Control Systems: }}{Git (Azure Repos, GitLab, GitHub)}




 %---------------Certification----------------------------

\vspace{2.5mm}


\section{\textbf{Certification}}

  \item{\textbf {Microsoft Certified: } DevOps Engineer Expert
  \item \textbf{Microsoft Certified: } Azure Fundamentals
  \item \textbf{Google Professional: } Cloud DevOps Engineer



%-------------------------------------------
\end{document}
